---
title: "Gettin Started with Shiny"
author: "Lars Schoebitz"
date: "22 March 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro

The purpose of this document is to document the steps taken to build my first Shiny app in R. 

## Building a Shiny App

The steps taken to build a Shiny App are copied from the following website: [Zev Ross - Know Your Data ](http://zevross.com/blog/2016/04/19/r-powered-web-applications-with-shiny-a-tutorial-and-cheat-sheet-with-40-example-apps/)]

### Shiny at its simplest

```{r app-1, eval=FALSE}

## load shiny library
library(shiny)

## build first app
server <- function(input, output, session) { }          # this is the server

ui <- basicPage("the is a real Shiny app")              # the user interface

shinyApp(ui = ui, server = server)                      # this launches the app


```

### Set up your user interface (UI)

- Shiny uses Twitter Bootstrap
- possibility to use HTML templates but much easier to use predefined layout functions
- we are using `sidebarLayout`
- other layout functions can be found [here](http://shiny.rstudio.com/articles/layout-guide.html)

```{r app-2, eval = FALSE}

## load shiny library
library(shiny)

## server
server <- function(input, output, session) { }      

## user interface
ui <- fluidPage(
    titlePanel("App with simple layout"),
    
    sidebarLayout(
        
        sidebarPanel(
            "Sidebar"
        ), #end sidebarpanel 
        
        mainPanel(
            "This is the main panel"
        ) #end mainpanel
    ) #end sidebarlayout
)

## launch the app

shinyApp(ui = ui, server = server) 


```

### Adding elements with tags$xxx

- HTML elements can be added by using HTML tages. [See here](http://shiny.rstudio.com/articles/tag-glossary.html) for catalogue
- usage: `tags$OBJECT`
    - `tags$p` for paragraph
    - `tags$blockquote` for a blockquote
- for some common tags, helper functions exist, e.g. `h1()` for heading 

```{r app-3, eval = FALSE}

## load shiny library
library(shiny)

## server
server <- function(input, output, session) { }    

## user interface
ui <-  basicPage(
    h1("Title without tages $."),  
    tags$h2("But, I could still use tags."),  
    tags$blockquote("blockquote requires tags, because it's less common than e.g. h1()."),  
    code("data.frame(a = 1:10, b = 1:10"),   
    tags$code("The above is just formatted as code, but is actually a character string.")
)

## launch the app
shinyApp(ui = ui, server = server)

```


### Layout your app Bootstrap’s grid system manually

- more about the bootstrap gridsystem and CSS [here](https://getbootstrap.com/examples/grid/)
- all Bootstrap layouts are 12 columns across and these columns can be grouped to make wider columns.
- this time we are using `fluidPage` instead of `basicPage` 

```{r app-4, eval = FALSE}

## load shiny library
library(shiny)

## server
server <- function(input, output, session) { }    

## user interface

ui <- fluidPage(
    
    fluidRow(
        column(6, offset = 1,
               tags$h1("Title in one row")
        )
    ),
    fluidRow(
        column(1,
               actionButton("button", "Click")
        ),
        column(6,
               p("Row 2, Column 2 (button is col 1)")
               )
    )
)

## launch the app
shinyApp(ui = ui, server = server)

```

### Style the user interface

- can choose exitsting themes or style yourself with CSS

#### Using existing theme

- Bootstrap offers a number of themes 
- the `shinythemes` package allows to take advantage of this
- only need to add a line of coe to `fluidPage` or `fixedPage` function
- `basicPage` is not supported because its not based opn Bootstrap
- [Click here](http://rstudio.github.io/shinythemes/) for a catalogue orf RStudio themes
- [Click here](http://bootswatch.com) for even more free themes for Bootstrap 

```{r app-5, eval = FALSE}

## load libraries
library(shiny)
library(shinythemes)

## server
server <- function(input, output, session) { }    

## user interface

ui <- fluidPage(theme = shinytheme("cosmo"),
                
                titlePanel("Use an existing theme"),
                
                sidebarLayout(
                    
                    sidebarPanel(
                        h3("Note the button is black. This is different from the previous app."),
                        actionButton("button", "A button")
                    ),
                    
                    mainPanel(
                        tabsetPanel(
                            tabPanel("Plot"),
                            tabPanel("Summary"),
                            tabPanel("Table")
                        )
                    )
                )
)

## launch the app
shinyApp(ui = ui, server = server)



```

#### Style yourself with CSS

- for now, I will use the existing themes and no own CSS stylesheets, however, documentation is available in the blogpost 

```{r app-6, eval = FALSE}

## do not use own CSS styles yet

## load libraries
library(shiny)
library(shinythemes)

## server
server <- function(input, output, session) { }    

## user interface



```


#### Add widgets to user interface (text boxes, sliders etc)

- checkout the [R Studio Widget Gallery](http://shiny.rstudio.com/gallery/widget-gallery.html) for an overview of widgets
- all widgets have unique input id (`ìnputId`)
    - text is `mytext`
    - slider is `myslider`
    - **input ids must be unique**
    
```{r app-7, eval = FALSE}

## load libraries
library(shiny)

## server
server <- function(input, output, session) { }    

## user interface
ui <- basicPage(
    h3("A couple of simple widgets that don't do anything yet"),
    
    # a slider
    
    sliderInput(inputId = "myslider", label = "Limit the ", min = 0, max = 100, value = c(40, 60)),
    
    # a text input box
    
    textInput(inputId = "mytext", label = "Text input", value = "Enter text...")
)

## launch the app
shinyApp(ui = ui, server = server)


```

### Setup the server

#### Input from your user inteface

- unique input ids
- all widgets have a unique ID that the server will listen for and react to
- each of the input ids is mapped to the `ìnput` argument on the server
    - if you want to access the value of the text box (`mytext`) from within the server, you would call `input$mytext`.
    - for the slider `input$myslider`
        - these objects are called reactive values
        

#### Listen for changes with observe or reactive, the Shiny hearing aids

- showing an example that doesn't work
- in summary: do not use `print(input$mytext)` in the server function because the reactive value is not being read by a function designed to handle it

#### introduce the update* functions

Using `updateTextInput` as a "console" for this blog post

```{r app-8, eval = FALSE}

## load libraries
library(shiny)

## server
server <- function(input, output, session) {
    
    observe({
        txt <- paste("Value above is:", input$mytext)
        
        # writing a result to the text box called myresults
        updateTextInput(session = session, inputId = "myresults", value = txt)
    })
}    

## user interface
ui <- basicPage(
    h3("An example of an update* function"),
    
    textInput(inputId = "mytext", label = "Input goes here"),
    
    textInput(inputId = "myresults", label = "Results will be printed here", value = "Initial value" )
)

## launch the app
shinyApp(ui = ui, server = server)



``` 

#### Back to functions to read reactive values: featuring observe to generate side effects and no output

- don't use `observe()` function to return data or values
    - that's what the `reactive()` function is for

```{r app-9, eval = FALSE}

## load libraries
library(shiny)

## server
server <- function(input, output, session) {
    
    observe({
        updateTextInput(session = session, inputId = "myresults", value = input$mytext)

    })
}    

## user interface
ui <- basicPage(
    h3("The value in the text box gets printed to the results text box."),
    textInput(inputId = "mytext", label = "Input goes here"),
    textInput(inputId = "myresults", label = "Results will be printed here", value = "Initial value")
)

## launch the app
shinyApp(ui = ui, server = server)

    
```

##### Example app: All the reactive values in observe will trigger the code to run (even if that’s not what you want)

- an example of something that we don't want to do!

```{r app-9, eval = FALSE}

## load libraries
library(shiny)

## server
server <- function(input, output, session) {
    
    observe({
        # even though the slider ius not involved in a calculation, if the slider is changed
        # it will run all this code and update the text box changes
        # to the mxtext box also will trigger the code to run
        input$myslider
        txt <-  paste(input$mytext, sample(1:10000, 1))
        updateTextInput(session = session, inputId = "myresults", value = txt)

    })
}    

## user interface
ui <- basicPage(
    h3("The results textbox gets updated if we change the other textbox or the slider"),
    sliderInput(inputId = "myslider", label = "A slider:", min = 0, max = 1000, value = 500),
    textInput(inputId = "mytext", label = "Input goes here", value = "Initial value"),
    textInput(inputId = "myresults", label = "Results will be printed here")
)

## launch the app
shinyApp(ui = ui, server = server)

    
```


##### Example app: Only specified reactive(s) trigger the code to run using observeEvent.

- same code as above, but not using `observeEvent` instead of `observe` 

```{r app-10, eval = FALSE}

## load libraries
library(shiny)

## server
server <- function(input, output, session) {
    
    # Using observeEvent we are telling Shiny only to run this code if mytext gets updated
    observeEvent(eventExpr = input$mytext, {
        
        # myslider is a reactive object but it does not trigger the code to run
        # here because we are using observeEvent and only specified
        # input$mytext
        input$myslider
        txt <-  paste(input$mytext, sample(1:10000, 1))
        updateTextInput(session = session, inputId = "myresults", value = txt)

    })
}    

## user interface
ui <- basicPage(
    h3("The results text box only updated when you change the top text box."),
    sliderInput(inputId = "myslider", label = "A slider:", min = 0, max = 1000, value = 500),
    textInput(inputId = "mytext", label = "Input goes here", value = "Initial value"),
    textInput(inputId = "myresults", label = "Results will be printed here")
)

## launch the app
shinyApp(ui = ui, server = server)

    
```

##### Observer priority: which observers run first

- when no priority is specified, then second observer will run second and overwrite the first observer

```{r app-11, eval = FALSE}

## load libraries
library(shiny)

## server
server <- function(input, output, session) {
  
  # With no priority specified the second observer will
  # run second and overwrite the first observer
  observe({
    txtA <- paste("First observer", input$mytext)
    updateTextInput(session, inputId = "myresults", value = txtA)
  })
  
  observe({
    txtB <- paste("Second observer", input$mytext)
    updateTextInput(session, inputId = "myresults", value = txtB)
  })
  
  
}

ui <- basicPage(
  h3("Second observer runs second so it overwrites the first observer"),
  textInput("mytext", "Input goes here"),
  textInput("myresults", "Results will be printed here", "Initial value")
)

shinyApp(ui = ui, server = server)
    
    
```

##### Example app: Prioritize to control order of execution

- use priority argument in `updateTextInput`

```{r app-12, eval = FALSE}

server <- function(input, output, session) {
  
  # first observer has lower priority so it runs second and will
  # overwrite the other observer
  observe({
    txtA <- paste("First observer", input$mytext)
    updateTextInput(session, inputId = "myresults", value = txtA)
  }, priority = 1)
  
  # second observer has higher priority so it will run first and
  # then be overwritten
  observe({
    txtB <- paste("Second observer", input$mytext)
    updateTextInput(session, inputId = "myresults", value = txtB)
  }, priority = 2)
  
}

ui <- basicPage(
  
  h3("Priority is higher for second observer so it runs first and then gets written over by the first observer"),
  textInput("mytext", "Input goes here"),
  textInput("myresults", "Results will be printed here", "")
)

shinyApp(ui = ui, server = server)


```

#### reactive: use a reactive function to isolate code and generate output with no side effects

```{r app-13, eval = FALSE}

server <- function(input, output, session) {
  
  # this is my reactive function -- I'm using it to
  # isolate reactions related to the text box
  mystring <- reactive({
    paste(input$mytext, " is what the user types")
  })
  
  observe({
    # The reactive will run each time the textbox changes and
    # print results to the console.
    txt <- mystring()
    updateTextInput(session, inputId = "myresults", value = txt) 
  })
  
}

ui <- basicPage(
  
    h3("The reactive generates a string output which is added to the results text box"),
    textInput("mytext", "Input goes here"),
    textInput("myresults", "Results will be printed here", "")

)

shinyApp(ui = ui, server = server)



```

#### eventReactive: used to prevent unwanted reactions in a reactive function

```{r app-14} 



```

