---
title: "A Multi-page HTML Document"
author: "Lars Schoebitz"
date: "`r Sys.Date()`"
output:
  pagedown::html_paged: 
    css: ["CSS/custom-fonts.css", "CSS/custom-page.css", "CSS/custom.css"]
    #front_cover: !expr system.file("img", "Rlogo.png", package="png")
    #back_cover: https://www.r-project.org/Rlogo.png
    toc: true
    toc-title: "My TOC"
    lot: true
    # default: "List of Tables"
    lot-title: "Tables"
    lof: true
    # default: "List of Figures"
    lof-title: "Figures"
chapter_name: ["CHAPTER\\ ", "."]
paged-footnotes: true 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

## Learning resource: https://www.r-project.ro/conference2019/presentations/Lesur2.pdf
## make a copy of default stylesheets

# files <- c("default-fonts", "default-page", "default")
# from <- pagedown:::pkg_resource(paste0("css/", files, ".css"))
# to <- c("CSS/custom-fonts.css", "CSS/custom-page.css", "CSS/custom.css")
# file.copy(from = from, to = to)

```




:::front-cover
# My great book about
:::

:::back-cover
### Written with love
:::


# Introduction

This is an example of a multi-page HTML document. See https://pagedown.rbind.io for the full documentation. The rest of this document is random text.

# Random text {.chapter}

## Second level heading

Basic text

## A plot

Refer to Figure \@ref(fig:plot1) in the text.

```{r plot1, fig.cap="Caption for Plot 1"}

library(tidyverse)

ggplot(mtcars, aes(x = cyl, y = mpg, group = cyl)) +
    geom_boxplot()

```

## A table

Refer to Table \@ref(tab:table1) in the text.

```{r table1, }


knitr::kable(head(iris[, -5]), caption = 'An example table.')

```

## Hyperlinks and footnotes

Here is a hyperlink to [my website](www.lse.de). Another website^[www.lse.de] link.
