---
title: "Learning xaringan"
subtitle: "test slides"
author: "Lars Schoebitz"
date: "23 January 2017"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      ratio: '16:9'
      highlightStyle: github
      highlightLines: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

# 2nd slide

- bullet one
  - bullet two
  
1. hi
3. hi again

---
# 3rd slide

- testing now code from interactive-docs.Rmd
  - text below box does not respond to change

```{r bsselectR, echo = FALSE}

library(bsselectR)

quotes <- c("Look deep into nature, and then you will understand everything better.", 
            "A fool thinks himself to be wise, but a wise man knows himself to be a fool.", 
            "My mission in life is not merely to survive, but to thrive; and to do so with some passion, some compassion, some humor, and some style.")

names(quotes) <- c("Einstein", "Shakespeare", "Angelou")

bsselect(quotes, type = "text")

```

---
# 4th slide

- just adding a bit of R code

```{r}

head(cars)


```

---
# 5th slide - ggplot2

- adding a plot
  - figure out how to change ratio of plot

```{r plot, echo = FALSE}

library(ggplot2)

ggplot(cars, aes(x = speed, y = dist)) +
  geom_point(stat = "identity") +
  theme_bw(base_size = 30)

```

---
# 6th slide

- writing in two columns

.pull-left[
- write some text
- and some more
- can even make a footnote `*`
]

.pull-right[
1. ordered list
1. another point
1. and a third one
]

.footnote[[*] Not really. See next page.]

---
# 7th slide

.pull-left[
```{r plot2, echo = FALSE, cache = TRUE}

ggplot2::ggplot(cars, aes(y = speed, x = dist)) +
  geom_point(stat = "identity") +
  theme_bw(base_size = 15)

```
]

.pull-right[
1. ordered list
1. another point
1. and a third one
]

---
# 8th slide
- using leaflet
  - **learn about leaflet coordinates**

```{r out.width='100%', fig.height=6, eval=require('leaflet')}
library(leaflet)
leaflet() %>%
  addTiles() %>%
  setView(-93.65, 42.0285, zoom = 17)


```


