---
title: "Untitled"
format: html
editor: source
editor_options: 
  chunk_output_type: console
---

# Resources

- https://observablehq.com/@observablehq/data-wrangling-with-arquero-from-r
- https://quarto.org/docs/interactive/ojs/

# Goal

Reproduce examples from a slideshow that let's me show a plot from a Google Forms survey instantanously on a slide.

- https://github.com/larnsce/talk-runapp-quarto-2022/blob/main/index.qmd#L154
- https://github.com/larnsce/talk-runapp-quarto-2022/blob/main/index.qmd#L448

# Get started

```{r}
library(palmerpenguins)
library(tidyverse)

penguins <- penguins
ojs_define(data = penguins)
```

```{ojs}
2 * 3
```

```{r}
df <- data.frame(
  year = 1961:1990,
  max = runif(30, -10, 20) |> cumsum()
  )

ojs_define(df = df)
```

```{ojs}
Inputs.table(transpose(df), { sort: "year", reverse: true })
```

```{ojs}
Plot.plot({
  marks: [
    Plot.line(transpose(df), {x: "year", y: "max"})
  ]
})
```

# Live Google Sheet Example

```{ojs}
md`## Poll results (Respondents: ${respondentCount})`
```

```{ojs}
import { liveGoogleSheet } from "@jimjamslam/live-google-sheet";
import { aq, op } from "@uwdata/arquero";

surveyResults = liveGoogleSheet(
  "https://docs.google.com/spreadsheets/d/e/" +
    "2PACX-1vQy00FtSctLJDk0x6IuBhAgSzc21miDTB3MLjg3zJpx8kMqR2dnjAj4i0hmXlFUCz5VK7ae_ZSHa63_/" +
    "pub?gid=2042451149&single=true&output=csv",
  15000, 2, 3);

respondentCount = surveyResults.length;


```

```{ojs}
// get the counts of people using and interested in tools
countsUsed = aq.from(surveyResults)
  .derive({ used: d => op.split(d.responseUsed, ", ") })
  .select("used")
  .unroll("used")
  .groupby("used")
  .count()
  .derive({ measure: d => "Have used" })
  .rename({ used: "tool" })
```

```{ojs}
countsWant = aq.from(surveyResults)
  .derive({ want: d => op.split(d.responseWant, ", ") })
  .select("want")
  .unroll("want")
  .groupby("want")
  .count()
  .derive({ measure: d => "Want to learn" })
  .rename({ want: "tool" })
```

```{ojs}
// combine the two counts into one dataset again
countsAll = [...countsUsed.objects(), ...countsWant.objects()];

plotUsed = Plot.plot({
  marks: [
    Plot.barX(countsAll, { y: "tool", x: "count", fill: "tool" }),
    Plot.ruleX([respondentCount], { stroke: "#ffffff99" })
  ],
  x : { label: "" },
  y : { label: "", tickSize: 0 },
  facet: { data: countsAll, x: "measure", label: "" },
  marginLeft: 140,
  style: {
    width: 1350,
    height: 500,
    fontSize: 12,
  }
});
```

## How to create a live Google Sheet

That was pretty straight forward. File -> Share -> Publish to Web

## How to QUERY the form response to get custom column names

https://webapps.stackexchange.com/a/130490

- Make a new sheet
- Call it QUERY
- decide for your column names
- then use `QUERY()` formula and select the column headings in "Form Responses 1" Sheet
- then, File -> Share -> Publish to Web

