---
title: "Twilio Package"
author: "Lars Schoebitz"
date: "3/9/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Twilio

I found twilio through this blogpost: http://seankross.com/2017/03/07/Send-a-Text-from-R-with-Twilio.html

## set-up

Firstly, get an account on:

Then, get your SID and token.

- click on the dropdown menu on the top right corner
- then click "Account" and you will see your Account Settings
- go to API Credentials and then note the TEST credentials
    - to see the TEST ATHTOKEN, click on the eye next to the hidden characters
- verify your phone number under "User Settings" on the left
- click on "trial restrictions" in the top right corner
    - click on "get your first twilio phone number" under step 2 of getting started
    - set up a phone number that can receive and send SMS


Install the package: 

`install.packages("twilio")`

This can be done in the console.

Load the package and follow instructions

```{r}

library(twilio)

# First you need to set up your accound SID and token as environmental variables

Sys.setenv(TWILIO_SID = "AC9190304e7ef403670255af4f1e5a25a9")
Sys.setenv(TWILIO_TOKEN = "32899ff4863780bf0da175e4607f327d")

# Then we're just going to store the numbers in some variables
my_number <- "+41788240611"
twilio_number <- "+41798073668"

twilio::tw_send_message(my_number, twilio_number, "hey")

# this doesn't work
tw_send_message(to = "41788240611",
                from = "41790873668", 
                body = "Hello from R 👋")

 
```



