---
title: "openxlsx-package"
author: "Lars Schoebitz"
date: "24 May 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Code that I am playing around with here is taken from:

https://cran.r-project.org/web/packages/openxlsx/vignettes/Introduction.pdf

```{r}

library(openxlsx)
library(tidyverse)

```

## Overview of functions

### Write to working directory

Writes the iris datset (dataframe) into a worksheet and names the file as specified in the file argument. 

Does not give the worksheet a name.

```{r}

write.xlsx(iris, file = "writeXLSX1.xlsx")

```


### Write several dataframes

Write a list of data.frames to individual worksheets using list names as worksheet names.

```{r}

l <- list("IRIS" = iris, "MTCARS" = mtcars)

write.xlsx(l, file = "writeXLSX2.xlsx")



```

### Styling parameters

`write.xlsx` also accepts styling parameters. The simplest way is to set default options and set column class.


```{r}

options("openxlsx.borderColour" = "#4F80BD")
options("openxlsx.borderStyle" = "thin")
options("openxlsx.dateFormat" = "mm/dd/yyyy")
options("openxlsx.datetimeFormat" = "yyyy-mm-dd hh:mm:ss")
options("openxlsx.numFmt" = NULL) ## For default style rounding of numeric columns
df <- data.frame("Date" = Sys.Date()-0:19, "LogicalT" = TRUE,
"Time" = Sys.time()-0:19*60*60,
"Cash" = paste("$",1:20), "Cash2" = 31:50,
"hLink" = "https://CRAN.R-project.org/",
"Percentage" = seq(0, 1, length.out=20),
"TinyNumbers" = runif(20) / 1E9, stringsAsFactors = FALSE)
class(df$Cash) <- "currency"
class(df$Cash2) <- "accounting"
class(df$hLink) <- "hyperlink"
class(df$Percentage) <- "percentage"
class(df$TinyNumbers) <- "scientific"
write.xlsx(df, "writeXLSX3.xlsx")
write.xlsx(df, file = "writeXLSXTable3.xlsx", asTable = TRUE)

```

